% english abstract
\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   
   When observing and talking with owners of private parking lots, as well as with drivers, two major problems faced by these two groups were noticed. Owners and managers of private parking lots have reported a need to increase efficiency and, at the same time, lower their business costs. The drivers point out the time spent searching for parking spaces and the lack of a way to make a reservation on a parking lot as the main reasons for dissatisfaction with services offered by private parking.

   Taking this problems into account, it was possible to realize the one is the complement of the other, and to solve one of the problems you need to solve the other too. This has led to the realization that creating a kind of parking lot auction can be a good business opportunity. The project plan for the implementation of this solution was developed in this work.

   The creation of two applications were proposed. One to be used by the driver, where it is possible to make reservations and find vacant parking lots. The other application focuses on the owner or manager of the private parking, and allows you to check parking occupancy, peak times, check in and check out customers, generate trend reports, and other features.

   This project plan was based on the knowledge proposed in the fifth edition of \cite{project2013guia}. This work's organization follows the process groups and the areas of knowledge for each created document. The plan focuses on presenting and describing the processes used during this project management.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Keywords}: latex. abntex. text editoration.
 \end{otherlanguage*}
\end{resumo}